Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-15 robdml.tex
tex

Apart from that, our method outperforms the
previous methods in every aspect, as shown in \cref{fig:introplot} for 
example.
%
Although HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach
a higher ERS, they are excluded from comparison because they induce a
significant performance drop in R@1.

>>>>

Apart from that, our method outperforms the previous methods in every important
aspect, \ie, ERS, training cost (efficiency), and R@1, as shown in
\cref{tab:sota}.
%
HM[$\mathcal{R},\mathcal{M}$] and HM[$\mathcal{R},g_\mathsf{LGA}$] can reach a
higher ERS, but are excluded from comparison due to significant performance
drop in R@1.
